On the Synchronization Power of the OpenFlow Data Plane

### 2015-05-22 inband-sync.tex
bundle flags

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. 
In the mask, certain header fields, e.g., port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
For examples, \texttt{src=10.1.14.0, ff.ff.ff.f0} matches all packets
with source addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.
Certain field, such as \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
filed for performing conditional operations on  its content.   
\petr{Example?}

@@

%When properly configured,
Bundle execution is considered \emph{controller-atomic} 
in the sense that all controllers can observe switch states (configurations) that either \emph{before} or \emph{after} the
bundle (i.e., all its commands) are executed. 
By specifying the flag \texttt{ofpbf\_atomic},  
a bundle can also be  \emph{packet-atomic}, in a similar sense, which can prevent packets to being processed by intermediate (possibly invalid) configuration during a bundle.
In addition, by specifying the flag \texttt{ofpbf\_ordered},  bundle commands are executed according to the order they were added to the bundle, thereby allowing to perform dependent actions inside a bundle.
%\liron{i added controller atomicity and order preservation, see that it make sense...}

@@

\begin{enumerate}
\item \textbf{Example 1: Handling complex dependencies.} Let us consider two controllers
in charge
of \emph{load-balancing}.
In a load-balancing application, seemingly independent actions, defined over
completely independent logical flow spaces (say, two flows with source IP address ranges $1*$ and $0*$),
may in fact be dependent due to collocation in the underlying physical network.
If the two controllers concurrently and independently
update forwarding rules,
they may involuntarily
unbalance the flow allocation, as the managed flows are embedded
on the same physical links.
Flow space overlap checks cannot be used to detect
such conflicts.

@@

\item \textbf{Example 2: Supporting modifications.} 
Consider the problem of modifying previously installed forwarding rules.
While a bundle allows to conditionally add new rules or remove
old rules (and, using the flow space overlap
check feature $\checko$, to abort the transaction if potentially conflicting
rules were already there), it is not straightforward how to use it to  
modify existing rules, especially provided a specific condition.
In other words, the bundle and overlap check only help
for the \emph{conditional creation} of rules, not their \emph{modification}.
\end{enumerate}

>>>>

More precisely, the match part of a rule is 
a ternary pattern over packet \emph{header} fields.
The pattern is represented as a \emph{value} and a \emph{mask}. 
In the mask, certain header fields, e.g., port numbers or destination and source
addresses, can be \emph{wildcarded}, stipulating that their content does
not affect the match. 
Certain field, such as \emph{src}, \emph{dst}, \emph{metadata}, can be arbitrarily
bitmasked. 
In our implementations, we are going to use bitmasking of the metadata
field for performing conditional operations on  its content.   
For examples, \texttt{port=10.1.14.0, ff.ff.ff.f0} matches all packets
with source addresses in the range \texttt{10.1.14.0}--\texttt{10.1.14.127}.

@@

%When properly configured,
Bundle execution is considered \emph{controller-atomic} 
in the sense that all controllers can only observe switch 
configurations \emph{before} or \emph{after} the
bundle commands are executed. 
We set the flag \texttt{ofpbf\_atomic},  
making bundles \emph{packet-atomic}, 
in the sense that every data-plane packet is processed by a configuration
before or after the bundle, and not by a configuration resulting from
an incomplete bundle execution.
We also set the flag \texttt{ofpbf\_ordered},  to make sure that the 
bundle commands are executed in the order they were added to the
bundle, thereby respecting dependencies between bundle commands.
%\liron{i added controller atomicity and order preservation, see that it make sense...}

@@

%\begin{enumerate}
\vspace{2mm}
\noindent \textbf{Example 1: Handling complex dependencies.} Let us consider two controllers
in charge
of \emph{load-balancing}.
In a load-balancing application, seemingly independent actions, defined over
completely independent logical flow spaces (say, two flows with source IP address ranges $1*$ and $0*$),
may in fact be dependent due to collocation in the underlying physical network.
If the two controllers concurrently and independently
update forwarding rules,
they may involuntarily
unbalance the flow allocation, as the managed flows are embedded
on the same physical links.
Flow space overlap checks cannot be used to detect
such conflicts.

@@

\vspace{2mm}
\noindent\textbf{Example 2: Supporting modifications.} 
Consider the problem of modifying previously installed forwarding rules.
While a bundle allows to conditionally add new rules or remove
old rules (and, using the flow space overlap
check feature $\checko$, to abort the transaction if potentially conflicting
rules were already there), it is not straightforward how to use it to  
modify existing rules, especially provided a specific condition.
In other words, the bundle and overlap check only help
for the \emph{conditional creation} of rules, not their \emph{modification}.
